Effects of Water Permeability on the Hydrodynamics of a Vesicle Under Flow and Confinement

### 2020-12-21 vesicle_code/docs/permeableVes/main.tex
added some flow velocities to stenosis example

We consider both an impermeable and semi-permeable vesicle
with initial reduced area $\alpha = 0.65$ passing through a long narrow channel
and compute the excess pressure as a function of vesicle position in the channel, see Figure~\ref{fig:stenosisComposite}(c). 
The impermeable case agrees with experimental
results in Figure 3 of \cite{abk-fai-sto2006}, and the results indicate
that less excess pressure is required to maintain a constant flow rate when the
vesicle is semi-permeable. First we note that the vesicle deflates from the beginning due to the high flow velocity, consistent with the results for a vesicle in a Poiseuille flow in open space. {\bf YNY: What is the flow velocity in the inlet/outlet? need to specify these to make connection to the phase diagram in the Poiseuille flow section.}
As the vesicle enters the stenosis channel, the vesicle continues to deflate in the front even though we observe influx (red segment) at various rear locations in the membrane. 
These results are consistent with the results in \cite{Pak2015_PNAS} where the membrane tension is sufficiently large in the front of the vesicle as it goes through a constrictive channel.

>>>>

We consider both an impermeable and semi-permeable vesicle with initial
reduced area $\alpha = 0.65$ passing through a long narrow channel and
compute the excess pressure as a function of vesicle position in the
channel, see Figure~\ref{fig:stenosisComposite}(c). A constant
Poiseuille velocity with a maximum value of $1000\mu$m/s is maintained
at the inlet and outlet. The impermeable case agrees with experimental
results in Figure 3 of~\cite{abk-fai-sto2006}, and the results indicate
that less excess pressure is required to maintain a constant flow rate
when the vesicle is semi-permeable. First we note that the vesicle
deflates from the beginning due to the high flow velocity, consistent
with the results for a vesicle in a Poiseuille flow in open space. As
the vesicle enters the stenosis channel, the vesicle continues to
deflate in the front even though we observe influx (red segment) at
various rear locations in the membrane.  These results are consistent
with the results in~\cite{Pak2015_PNAS} where the membrane tension is
sufficiently large in the front of the vesicle as it goes through a
constrictive channel.
